
```{r echo=FALSE, results='hide',message=FALSE, warning=FALSE}

x <- c("plyr","dplyr","ggplot2","RColorBrewer", "wordcloud","gridExtra", "plotrix","pander")

lapply(x, require,character.only = TRUE)

setwd('D:/Float/20160712')
load('usum.Rdata')
load('RiskView.Rdata')
data_total <- read.csv('people_export_2016_06_15.csv')

```

# Age vs. No of customers

```{r echo=FALSE}
a <- count(usum,age)  

usum_age <- usum %>% filter(age>=19,age<=36)
Count_age <- as.data.frame(count(usum_age,age))
qplot(age, data=Count_age,weight=n, geom="histogram", binwidth=1)

```

We observe customers between ages 19 to 36 are significant. Hence we take customers only from this age group


# age vs. bank transactions data

# age vs. income

```{r echo=FALSE ,message=FALSE, warning=FALSE}

charts_bank <- usum_age %>% group_by(age) %>% summarise(avg_income = mean(income.averageMonthly),
                                                        avg_months = mean(months),
                                                        avg_RVscore = mean(RVbankCard),
                                                        avg_spending = mean(spending.averageMonthly),
                                                        avg_overdrafts_month = mean(overdrafts.count.monthly))


print(ggplot(data = charts_bank,aes(charts_bank[,1],charts_bank[,2])) + geom_point() + geom_smooth(method =  "lm") +
          xlab(colnames(charts_bank)[1]) + ylab(colnames(charts_bank)[2]) +  ggtitle(paste(colnames(charts_bank)[2],"vs.", colnames(charts_bank)[2])) + theme_classic())
  
lm0 <- lm(avg_income ~ age, data=charts_bank)


# r.squared
print("rsquare")
print(summary(lm0)$r.squared)
# p value
print("P value")
print(summary(lm0)$coefficients[2,4])

```



# age vs. months of data availability

```{r echo=FALSE ,message=FALSE, warning=FALSE}


print(ggplot(data = charts_bank,aes(charts_bank[,1],charts_bank[,3])) + geom_point() + geom_smooth(method =  "lm") +
          xlab(colnames(charts_bank)[1]) + ylab(colnames(charts_bank)[3]) +  ggtitle(paste(colnames(charts_bank)[3],"vs.", colnames(charts_bank)[3])) + theme_classic())
  
lm0 <- lm(avg_months ~ age, data=charts_bank)


# r.squared
print("rsquare")
print(summary(lm0)$r.squared)
# p value
print("P value")
print(summary(lm0)$coefficients[2,4])

```


# age vs. RVScore

```{r echo=FALSE ,message=FALSE, warning=FALSE}


print(ggplot(data = charts_bank,aes(charts_bank[,1],charts_bank[,4])) + geom_point() + geom_smooth(method =  "lm") +
          xlab(colnames(charts_bank)[1]) + ylab(colnames(charts_bank)[4]) +  ggtitle(paste(colnames(charts_bank)[4],"vs.", colnames(charts_bank)[4])) + theme_classic())
  
lm0 <- lm(avg_RVscore ~ age, data=charts_bank)


# r.squared
print("rsquare")
print(summary(lm0)$r.squared)
# p value
print("P value")
print(summary(lm0)$coefficients[2,4])

```


# age vs. spending

```{r echo=FALSE ,message=FALSE, warning=FALSE}


print(ggplot(data = charts_bank,aes(charts_bank[,1],charts_bank[,5])) + geom_point() + geom_smooth(method =  "lm") +
          xlab(colnames(charts_bank)[1]) + ylab(colnames(charts_bank)[5]) +  ggtitle(paste(colnames(charts_bank)[5],"vs.", colnames(charts_bank)[5])) + theme_classic())
  
lm0 <- lm(avg_spending ~ age, data=charts_bank)


# r.squared
print("rsquare")
print(summary(lm0)$r.squared)
# p value
print("P value")
print(summary(lm0)$coefficients[2,4])

```


# age vs. Overdrafts_month

```{r echo=FALSE ,message=FALSE, warning=FALSE}


print(ggplot(data = charts_bank,aes(charts_bank[,1],charts_bank[,6])) + geom_point() + geom_smooth(method =  "lm") +
          xlab(colnames(charts_bank)[1]) + ylab(colnames(charts_bank)[6]) +  ggtitle(paste(colnames(charts_bank)[6],"vs.", colnames(charts_bank)[6])) + theme_classic())
  
lm0 <- lm(avg_overdrafts_month ~ age, data=charts_bank)


# r.squared
print("rsquare")
print(summary(lm0)$r.squared)
# p value
print("P value")
print(summary(lm0)$coefficients[2,4])

```

#Observations

1. As expected average income and spending is increasing with increase in age  
2. Average overdrats per month is increasing with increase in age  
3. There is No trend in RVScore and age. Average RV Score for all ages lies between ~625 to ~650  
4. There is slight relationship between months and age. Months increase with increase in age  


```{r echo=FALSE , message=FALSE, warning=FALSE}
# selecing only required columns
data_select <- select(data_total, X.distinct_id, campaign, media_source, city,state,Daily_Balance,X.region)

data_RV <- select(RV,id, EducationFieldofStudyType
                  ,EducationInstitutionRating
                  ,EstimatedAnnualIncome
                  ,PropertyOwner
                  ,AssetOwner
                  ,WealthIndex
                  ,DerogCount
                  ,DerogRecentCount
                  ,DerogSeverityIndex
                  ,InquiryCollectionsRecent,
                  AddrStability,
                  InputAddrMortgageType,
                  CurrAddrDwellType,
                  AddrRecentEconTrajectoryIndex,
                  BusinessTitle,
                  DerogRecentCount,
                  RecentActivityIndex,
                  ProfLicCount,
                  InquiryPersonalFinanceRecent,
                  HighRiskCreditActivity,
                  EmailAddress,
                  InputAddrHighRisk)

data_RV <- data.frame(lapply(data_RV,function(x) as.numeric(x)))

data_RV$id <- RV$id
data_RV$CurrAddrDwellType <- RV$CurrAddrDwellType
data_RV$BusinessTitle <- RV$BusinessTitle


colnames(data_select)[1] <- colnames(usum_age)[1]
colnames(data_RV)[1] <- colnames(usum_age)[1]

usum_age1 <- inner_join(usum_age, data_select, by = c('id'))
usum_age2 <- inner_join(usum_age1, data_RV, by = c('id'))
```

#Education Field of study

Indicates the field study type-grouped based on similar areas of study and average incomes for occupations typically associated with those fields of study

-1 ---> Field of study is not on file  
0 ----> Field of study is uncategorized  
Group 1 (i.e. Art, Music)  
Group 2 (i.e. Education, Humanities, Religion, Social sciences, Liberal Arts, English, Journalism)  
Group 3 (i.e. Business, Accounting, Marketing, Finance Management)  
Group 4 (i.e. Biological Science, Physical Science,Biology)  
Group 5 (i.e. Engineering, Computers, Architecture)  
Group 6 (i.e. Law, Legal Studies)  
Group 7 (i.e. Health professions, Nursing, Medicine,Chiropractic)  

```{r echo=FALSE ,message=FALSE, warning=FALSE}

panderOptions('round', 2)
panderOptions('keep.trailing.zeros', TRUE)
pander(prop.table(addmargins(table(usum_age2$age,usum_age2$EducationFieldofStudyType), margin = 1),1))
```

#Observations

1. About 82% of the people have "Field of study is not on file" and it is predominant in the younger people (19, 20 and 21)
2. We observed similar trends in other groups as well. Only 5% of people have "field of study" has categorized

#Education Institution Rating

Indicates the education program rating based on various institution statistics and national ratings (Tier 1 = highest rating, Tier 6 =lowest rating)

-1 ---> Information not on file 
0 ---> Unknown 
1 ---> Tier 1 rating  
2 ---> Tier 2 rating  
3 ---> Tier 3 rating  
4 ---> Tier 4 rating  
5 ---> Tier 5 rating  
6 ---> Tier 6 rating  

```{r echo=FALSE ,message=FALSE, warning=FALSE}

panderOptions('round', 2)
panderOptions('keep.trailing.zeros', TRUE)
pander(prop.table(addmargins(table(usum_age2$age,usum_age2$EducationInstitutionRating), margin = 1),1))

```


#Observations

1. About 82% of the people have "information not on file" and it is predominant in the younger people (19, 20 and 21)
2. We observed similar trends in other groups as well. when we dig deep into other categories we found that most people are from tier 3, 4 or 5 categories. Very few people are from tier 1 adn tier 2 category schools.


#Address Stability

Address stability index indicating how often subject has changed addresses

0 --> unknown  
(1 = High evidence of instability to 6 = High evidence of stability)  

```{r echo=FALSE ,message=FALSE, warning=FALSE}

panderOptions('round', 2)
panderOptions('keep.trailing.zeros', TRUE)
pander(prop.table(addmargins(table(usum_age2$age,usum_age2$AddrStability), margin = 1),1))

charts_RV_AddrStability <- usum_age2 %>% group_by(age) %>% filter(AddrStability != 0) %>% summarise(AddrStability_avg = mean(AddrStability))

print(ggplot(data = charts_RV_AddrStability,aes(charts_RV_AddrStability$age,charts_RV_AddrStability$AddrStability_avg))+ geom_point() + geom_smooth(method =  "lm") + xlab('age') + ylab('AddrStability_Avg'))


lm0 <- lm(AddrStability_avg ~ age, data=charts_RV_AddrStability)


# r.squared
print("rsquare")
print(summary(lm0)$r.squared)
# p value
print("P value")
print(summary(lm0)$coefficients[2,4])


```

#Observations

1. Address stability index increasing with increase in age. Hence, people with high age are expected to have high scores on behalf of adress stability index


#Derog Count

Total derogatory public records (felonies,liens, bankruptcies, and evictions)


```{r echo=FALSE ,message=FALSE, warning=FALSE}

charts_RV_DerogCount <- usum_age2 %>% group_by(age) %>% summarise(DerogCount_avg = mean(DerogCount))

print(ggplot(data = charts_RV_DerogCount,aes(charts_RV_DerogCount$age,charts_RV_DerogCount$DerogCount_avg))+ geom_point() + geom_smooth(method =  "lm") + xlab('age') + ylab('DerogCount_avg'))


lm0 <- lm(DerogCount_avg ~ age, data=charts_RV_DerogCount)


# r.squared
print("rsquare")
print(summary(lm0)$r.squared)
# p value
print("P value")
print(summary(lm0)$coefficients[2,4])

```

#Observations

1. We can clearly observe that dergortory records increases with increase in age  
2. Lets look at how severe these records are with respect to different age groups  

#DerogSeverityIndex

Severity index based on the type of derogatory record

0 --> No derogatory record on file  
1 --> Record contains released liens  
2 --> Record contains bankruptcies  
3 --> Record contains filed liens  
4 --> Record contains evictions  
5 --> Record contains felonies  
 


```{r echo=FALSE ,message=FALSE, warning=FALSE}

panderOptions('round', 2)
panderOptions('keep.trailing.zeros', TRUE)
pander(prop.table(addmargins(table(usum_age2$age,usum_age2$DerogSeverityIndex), margin = 1),1))

charts_RV_DerogSeverityIndex <- usum_age2 %>% group_by(age) %>% summarise(DerogSeverityIndex_avg = mean(DerogSeverityIndex))

print(ggplot(data = charts_RV_DerogSeverityIndex,aes(charts_RV_DerogSeverityIndex$age,charts_RV_DerogSeverityIndex$DerogSeverityIndex_avg))+ geom_point() + geom_smooth(method =  "lm") + xlab('age') + ylab('DerogSeverityIndex_avg'))

lm0 <- lm(DerogSeverityIndex_avg ~ age, data=charts_RV_DerogSeverityIndex)

# r.squared
print("rsquare")
print(summary(lm0)$r.squared)
# p value
print("P value")
print(summary(lm0)$coefficients[2,4])

```

#Observations

1. We can observe that overall about 22% of people have derogatory records  
2. About 11% of the people have bankruptcy records  
3. Most of the high severity indices are observed in elder people (average of severity index is increasing with age)  


#Derog Recent Count

Number of derogatory public records within the last 12 months


```{r echo=FALSE ,message=FALSE, warning=FALSE}

charts_RV_DerogRCount <- usum_age2 %>% group_by(age) %>% summarise(DerogRCount_avg = mean(DerogRecentCount))

print(ggplot(data = charts_RV_DerogRCount,aes(charts_RV_DerogRCount$age,charts_RV_DerogRCount$DerogRCount_avg))+ geom_point() + geom_smooth(method =  "lm") + xlab('age') + ylab('DerogRecentCount_avg'))


lm0 <- lm(DerogRCount_avg ~ age, data=charts_RV_DerogRCount)

# r.squared
print("rsquare")
print(summary(lm0)$r.squared)
# p value
print("P value")
print(summary(lm0)$coefficients[2,4])

```

#Observations

1. Similar trend can be observed for derogatory records in the last 12 months


#HighRiskCreditActivity

LexisNexis RiskView personal finance inquiries or requested offers for subprime credit services (Ex. short-term loans or high-rate credit cards) associated with the subject

0 ---> Subject has no other inquiries in the last 12 months   
1 ---> Subject has one or more other inquiries in the last 12 months  


```{r echo=FALSE ,message=FALSE, warning=FALSE}

charts_RV_HRCA <- usum_age2 %>% group_by(age) %>% summarise(HRCA_avg = mean(HighRiskCreditActivity))

print(ggplot(data = charts_RV_HRCA,aes(charts_RV_HRCA$age,charts_RV_HRCA$HRCA_avg))+ geom_point() + geom_smooth(method =  "lm") + xlab('age') + ylab('HRCA_avg'))

lm0 <- lm(HRCA_avg ~ age, data=charts_RV_HRCA)

# r.squared
print("rsquare")
print(summary(lm0)$r.squared)
# p value
print("P value")
print(summary(lm0)$coefficients[2,4])

```

#Observations

1. It is found to be high in customers between ages 23 - 30. Overall its is found to be increasing with age slightly

# Media Source

```{r echo=FALSE ,message=FALSE, warning=FALSE}

panderOptions('round', 2)
panderOptions('keep.trailing.zeros', TRUE)
pander(prop.table(addmargins(table(usum_age2$age,usum_age2$media_source), margin = 1),1))

```

#Wordcloud of media source 

```{r echo=FALSE,message=FALSE, warning=FALSE}
count1 <- count(usum_age2,media_source)
names <- as.list(count1[1])[[1]]
frequency <- as.list(count1[2])[[1]]
words <- names(frequency)
wordcloud(names,frequency,scale=c(2,0.5),colors=palette(),max.words = 10 )
```

#Wordcloud of top BusinessTitles


```{r echo=FALSE,message=FALSE, warning=FALSE}
count1 <- count(usum_age2,BusinessTitle)
pal2 <- brewer.pal(8,"Dark2")
names <- as.list(count1[1])[[1]]
names <- names[-1]
frequency <- as.list(count1[2])[[1]]
words <- names(frequency)
wordcloud(names,frequency,scale=c(3,0.5),colors=pal2, min.freq = 2)
```


